Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/sec3-experiment-design.tex
4.1增加了超参数对精度影响的说明
fix语法

\paragraph{Hyper-parameters}
We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
%
We picked the hyper-parameters of GNNs according to their popularity in their references \cite{kipf2017_gcn, li2015_ggnn, huang2018_gat, zhang2018_gaan}.
%
Unless otherwise mentioned, we used the same set of hyper-parameters for all the datasets. 
%
Some hyper-parameters (like dimensions of hidden vectors) were common in the four GNNs and we set them to the same values.
%
For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_x = \boldsymbol{v}_x$, $dim(\boldsymbol{h}^1_x)=64$, and $dim(\boldsymbol{h}^2_x)=\#Class$ (the number of classes in the dataset).
%
For GAT, the first GAT layer contained 8 heads, and the attention vector of each head had a dimension of 8.
%
The first GAT layer merged attention vectors of 8 heads by concatenating.
%
The second GAT layer used a single head with a dimension of $\#Class$.
%
For GGNN, we set $dim(\boldsymbol{h}^0_x) = dim(\boldsymbol{h}^1_x) = dim(\boldsymbol{h}^2_x) = 64$.
%
We used 8 heads in the both GaAN layers with $d_a=d_v=8$, and $d_m=64$.

% added by wangyupan, 2020-12-21 ----start----
In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
%
That is, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}. 
%
We trained for a maximum of 100k epochs. 
%
If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
%
We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
%
Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
% added by wangyupan, 2020-12-21 ----end----

>>>>

\paragraph{Hyper-parameters}
\label{sec:hyper-parameters}

We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
%
We picked the hyper-parameters of GNNs according to their popularity in their references \cite{kipf2017_gcn, li2015_ggnn, huang2018_gat, zhang2018_gaan}.
%
Unless otherwise mentioned, we used the same set of hyper-parameters for all the datasets. 
%
Some hyper-parameters (like dimensions of hidden vectors) were common in the four GNNs and we set them to the same values.
%
For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_x = \boldsymbol{v}_x$, $dim(\boldsymbol{h}^1_x)=64$, and $dim(\boldsymbol{h}^2_x)=\#Class$ (the number of classes in the dataset).
%
For GAT, the first GAT layer contained 8 heads, and the attention vector of each head had a dimension of 8.
%
The first GAT layer merged attention vectors of 8 heads by concatenating.
%
The second GAT layer used a single head with a dimension of $\#Class$.
%
For GGNN, we set $dim(\boldsymbol{h}^0_x) = dim(\boldsymbol{h}^1_x) = dim(\boldsymbol{h}^2_x) = 64$.
%
We used 8 heads in the both GaAN layers with $d_a=d_v=8$, and $d_m=64$.

% added by wangyupan, 2020-12-21 ----start----
In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
%
That was, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}. 
%
We trained for a maximum of 100k epochs. 
%
If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
%
We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
%
Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
% added by wangyupan, 2020-12-21 ----end----
